\thispagestyle{empty}
\newgeometry{left=3.7cm, right=3.7cm,bottom=4cm ,top=2cm}
\begin{abstract}
\begin{small}
%Two studies with the ATLAS experiment  at the Large Hadron Collider (LHC)  have been performed in this thesis: 
%the search for the neutral MSSM Higgs bosons and an investigation on the prospect for enhancing the sensitivity of this search by using track-based jet
%in alternative to the canonical calorimeter-based jet reconstruction.

In this thesis a search for the neutral Higgs bosons of the Minimal Supersymmetric extension of the Standard Model has been performed
in leptonic final states of decays into $\tau$ lepton pairs with the ATLAS detector  at the Large Hadron Collider (LHC). 
The prospects for enhancing the sensitivity of this search by using jet reconstruction based on inner detector   tracks as an
alternative to the canonical calorimeter-based jet reconstruction has been investigated, too.


The search for the neutral MSSM Higgs bosons $A$, $h$ and $H$ has been performed using proton-proton collisions data
provided by LHC during 2012  at a centre-of-mass energy
of 8~TeV which correspond to an integrated luminosity of 20.3$\,\text{fb}^{-1}$. The search focuses on  Higgs boson decays
into a pair of $\tau$ leptons which subsequently decays via  $\tau^+ \tau^- \rightarrow e \mu +4\nu$.
%The decay into $\tau$ leptons pair has the highest sensitivity for this search.
%The search is performed for the two most significant production modes, gluon fusion and the production in association with b-quarks. 
To enhance the signal sensitivity,  the   events are split into two mutually exclusive categories
without and with  b-tagged jets indicating the two dominant production mode via gluon fusion and in association with b-quarks, respectively.
The results are interpreted in terms of the  MSSM $m_h^{mod}$ benchmark scenario. 
No significant excess of event above the estimated Standard Model background has been found. 
Upper  limits on the production cross section time branching ratio into the final state have been derived in the plane
of the free MSSM parameters  $m_A$ and $\tan\beta$, where the latter is the ratio of the vacuum expectation values
of the two MSSM Higgs doublets. Values  of $\tan\beta \apprge 10$ are excluded in the mass range $90 < m_A < 200$~GeV. %something on limits
The highest local p-value of 2.9\% for the background only hypotesis is observed in the mass rage $250< m_A <300$~GeV 
which  corresponds to a $1.9\,\sigma$ excess.
In addition, less model-dependent upper limits on the production cross section for 
 a generic scalar boson $\phi$ with  mass  $m_\phi$ via the  processes $pp \rightarrow b\bar{b}\phi$ and $gg \rightarrow \phi$
have been derived.


The neutral MSSM Higgs bosons producion in association with b-quarks is characterised by the presence of  low transverse momentum
b-jets. The reconstruction and calibration of low transverse momenta jets from energy deposits in the calorimeters
 is strongly affected by pile-up effects due to the multiple proton interaction
per bunch crossing which become significant with the icrease of the instantaneus luminosity of the LHC in 2012.
An alternative approach employing jet reconstruction based on inner detector tracks for the identification of the b-jets
(b-tagging) have been  investigated. For jets with low transverse momenta the track-based jet reconstruction
provides a higher jet reconstruction efficiency than calorimeter-based  jets and are more suitable  for
low $\pt$ b-tagging. This preliminary study shows that the sensitivity for neutral MSSM Higgs boson producion 
in association with b-quarks can be improved by up to a factor two if track-based jet reconstruction is employed 
instead of the canonical calorimeter-based one. However, additional study are needed to fully estimate the
systematic uncertainty on track-based jets, furthermore a dedicated calibration of b-tagging algorithms 
is necessary for such a jet reconstruction tecchnique.
 

%This is one of the main reason for sensitivity loss of this search in the category that 
%requires a b-tagged jet. An alternative approach would be to use the so-called track-based jets reconstruction, 
%which relies only on identified inner detector tracks for the jet reconstruction.  The measure of inner detector tracks
%is very precise and is possible to associate them with the corresponding interaction vertex,  
%this feature makes track-based jets more robust against pile-up effects than calorimeter-based jets. 
%A study on the prospect for enhancing the sensitivity of the neutral MSSM 
%An alternative b-jet identification procedure in which the b-tagging algorithm is applied on 
%track-based jets instead on canonical calorimeter jets has been studied in this thesis.
%The calorimeter jets are reconstructed
%from the energy clusters in the calorimeter, while the track-based jets consist of inner detector tracks,
%the precise track information makes the latter considerably more robust to pile-up effects.
%The performance of the b-tagging algorithms on track-based jets is investigated for the first time.
%Systematic uncertainties on track-based jet reconstruction are also studied: one of the major systematic
%uncertainty arises from the mismodelling in simulation of the inner detector material (ID)  budget.
%A novel technique for addressing the ID material budget systematic uncertainty in track-jets energy scale and 
%reconstruction efficiency has been developed. For low transverse momentum track-jets uncertainty due to 
%material budget mismodelling in the energy scale is estimated to range from 2\% to 4\% depending on track-jet momentum and number of 
%associated tracks.
%It was shown that for jets with low transverse momentum the track-jets provide a higher
%b-hadron reconstruction efficiency than calorimeter jets and are more suitable  for
%low $\pt$ b-tagging. The sensitivity to the neutral MSSM Higgs boson produced in association with b-quarks can be improved 
% up to a factor two if track-jet reconstruction is applied instead of calorimeter based one.
%However, to exploit the full power of this technique a dedicated calibration of the 
%b-tagging algorithms is  needed for  track-based jets. 
\end{small}
\end{abstract}
\restoregeometry
