%\thispagestyle{empty}
%\begin{ackno}
%some shit
%\end{ackno}
\cleardoublepage
\renewcommand*{\chaptermarkformat}{}
  \chaptermark{Acknowledgments}
  \section*{\centering Acknowledgments}\thispagestyle{plain}\addtocontents{toc}{\protect\enlargethispage{2\normalbaselineskip}}\addcontentsline{toc}{chapter}{Acknowledgments}

First of all I would like to thank Prof. Hubert Kroha and Dr. Sandra Kortner for the precious comment and help 
during editing this document and to gave me the extraordinary opportunity of being here. 
I would like to thank the Max Planck Institute for the great opportinity I've had being here.
I also would like to thank the organizers of IMPRS with  a special thank to Frank Steffen.

I would like to thank the members of the neutral MSSM Higgs search analysis team, in particular 
Matthew Backingham and Nikolaos Rompotis, for being of such a great support during the last 
year.

I recived an incredible amount of support from many persons here, which may not be technical support but I lernt
to be equally precius. They made my stay here, in Munich, not only a pleasure,
not only an adventure, but have created an atmosphere that has the smell of home. It is to this big family that 
I want to address my most deep thanks. In order of appearance in this  fair tail that has been
my life here. To my almost russian roommate for cleaning the kitchen (maybe too many times) and to Mr. bamboo Toyama
with the  wish he wont be too ``heabi'' with the little Ko. To Shangy for being... himself, hoping one day he will find
his soul. To the Ogre for taching me the difference between pig and pork and to Fiona for being a good spezi.
To la Bruja Piruja, well, actually I don't know why she is in the list. To Sear-gay for the puzzling and oniric discussions.
But, most of all, I would like to thank the love of my life, the blond A.


Finally I would like to thank you, the reader, for being brave enough to arrive till this point of this document.

\begin{center}
{\LARGE THANKS!}
\end{center}

{\small I'm very sorry if I accidentally forgot someone and for the very poor quality of this acknowledgment...
but it is 4 am...}

